Sparse Function-space Representation \\ of Neural Networks

### 2023-05-10 paper/main.tex
started laplace section

\newcommand{\vm}{\mbf{m}}
%\newcommand{\vz}{\mbf{z}}
%\newcommand{\vf}{\mbf{f}}
\newcommand{\vu}{\mbf{u}}
\newcommand{\vx}{\mbf{x}}
\newcommand{\vy}{\mbf{y}}

@@

\textbf{Neural Network} A neural network takes ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ and fits a function $f(\mathbf{x}_{i};\transitionParams)$ through the following optimization:
\begin{align} \label{eq-empirical-risk}
  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{P}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{P}} \left(
  \sum_{i=1}^{N} l(f(\mathbf{x}_{i} ; \transitionParams), y_i) + \frac{1}{\delta}R(\transitionParams)  \right).
\end{align}
If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$

\textbf{Laplace approximation}

>>>>

\newcommand{\vm}{\mbf{m}}
%\newcommand{\vz}{\mbf{z}}
%\newcommand{\vf}{\mbf{f}}
\newcommand{\vu}{\mbf{u}}
\newcommand{\vx}{\mbf{x}}
\newcommand{\vy}{\mbf{y}}
\newcommand{\vw}{\mbf{w}}

@@

\textbf{Neural Network} Given the data set $\dataset_n = \{\mathbf{x}_{i} \in \inputDomain, y_{i} \in \outputDomain\}_{i=1}^{N}$,
the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
\begin{align} \label{eq-empirical-risk}
  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{P}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{P}} \left(
  \sum_{i=1}^{N} l(f(\mathbf{x}_{i} ; \transitionParams), y_i) + \frac{1}{\delta}R(\transitionParams)  \right).
\end{align}
If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$ and $R(\transitionParams) = \|\transitionParams\|^{2}$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \N(\vzeros,\delta\MI)$.

\textbf{Laplace approximation} The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}.
